Ignition of Fuel Beds by Firebrands

### 2022-06-18 manuscript1.tex
Submitted version

\newcommand{\TheTitle}{Sensitivities of Porous Beds and Plates to Ignition by Firebrands}
\renewcommand{\TheAuthors}{Derek Bean, David L. Blunck \\ \\ My contributions to this work included the design of the experiments, fabrication of the experimental apparatus, collecting data and/or supervising undergraduates who collected data, data analysis, conducting modelling efforts, and preparation of the manuscript.}

>>>>

\newcommand{\TheTitle}{Sensitivities of Porous Beds and Plates to Ignition by Firebrands}
\renewcommand{\TheAuthors}{Derek Bean, David L. Blunck \\ \\ My contributions to this work included the design of the experiments, fabrication of the experimental apparatus, collecting data and/or supervising undergraduates who collected data, data analysis, conducting modelling efforts, and preparation of the manuscript. \\ \\ Further details of the modeling conducted in this manuscript are contained in Chapter~\ref{chap:manuscript2}.
}

### 2022-06-18 manuscript2.tex
Submitted version

     The temperature evolution of the fuel bed over time was used to estimate the pyrolysis products. The calculations solved the heat diffusion equation (Equation~\ref{eqn:heatDiffusion} to observe the spatial and temporal evolution of the fuel bed temperatures. Calculations were conducted for 10 seconds for two reasons. First, the assumptions, that are outlined in the following section, reduce the accuracy of the model due to pyrolysis of the fuel bed in the experiment changing the fuel bed properties. Second, in absence of changes in fuel beds due to pyrolysis a simulation time of ten seconds provided sufficient insight into trends observed in the experiments. 
        \begin{equation}
            \frac{\partial \left(\rho h \right)}{\partial t} = \frac{\partial}{\partial x_{j}} \left( \alpha \frac{\partial h}{\partial x_{j}} \right)
            \label{eqn:heatDiffusion}
        \end{equation}
     The assumptions for the temperature modeling of the fuel bed are as follows:
        \begin{itemize}
            \item Fuel beds were considered to be non reacting. 
            \item Thermal properties of the fuel bed were considered independent of temperature.
            \item The temperature evolution of the fuel bed is symmetric around the centerline of the heater.
            \item The heat losses to the ambient are significantly less than the heat transfer from the heater. Thus, the interface between the fuel bed and air was considered insulated.
            \item The fuel bed was modeled as a solid with the thermal and physical properties either measured or derived from experimental measurements.
        \end{itemize}

@@

        \begin{equation}
            m \pder[\left( m Y_k \right)]{t} = \dot{m}_{k, gen} = V \dot{\omega}_k MW_k
        \end{equation}
        \begin{equation}
            mc_{v} \pder[T]{t} = \dot{Q} - \sum_{k} \dot{m}_{k,gen}u_k
        \end{equation}
    Where $Y_k$, $\dot{m}_{k}$, and  $\dot{\omega}_k$ are the mass fraction, mass generation rate, and generation rate of each species $k$ in the mechanism used. $V$ is the volume of the fuel bed material in the reactor. The species generation rates $ \dot{\omega}_k$ are determined from the reactions included in the mechanism. The mechanism used for pyrolysis contains four different types of chemical reactions. The equations used to calculate the reaction rates for an elementary reaction is:
        \begin{align}
            k_f &= AT^{b}e^{-E_a/RT}\\
            R_{f} &= [A][B]k_f 
        \end{align}
    Where $R_f$ is the forward reaction rate, $k_f$ the reaction rate constant, $E_a$ the activation energy, $b$ is the temperature exponent and $R$ is the gas constant. Similarly, the reaction rates for three body reactions are calculated as:
        \begin{align}
            R_f &= [A][B][M]k_f \\
            [M] &= \sum_{k}\epsilon_k C_k
        \end{align}
    Where $\epsilon_k$ and $C_k$ are the collision efficiency and concentration of each species, respectively. Fallof reaction rates are calculated using the reduced pressure $P$ defined as:
        \begin{equation}
            P = \frac{k_0[M]}{k_\infty}
        \end{equation}
    The reaction reaction rate is then calculated as:
        \begin{equation}
            k_f (T, P) = k_{\infty} \left( \frac{P}{1+P}\right) F(T,P)
        \end{equation}
      Pressure dependent P-Log reaction rates are calculated for intermediate values using a logarithmic interpolation between two reaction rates $k_1$ and $k_2$ at pressures $P_1$ and $P_2$ as:
        \begin{equation}
            \log k_f(T,P) = \log k_1(T) + (\log k_2(T) - \log k_1(T))\frac{\log P - \log P_1}{\log P_2 - \log P_1}
        \end{equation}
    The overall generation rate of each species ($\dot{\omega}_k$) is then defined as the sum of the individual reaction rates $R_f$ for all of the reactions where the species is present. 
        \begin{equation}
            \dot{\omega}_k = \sum_i^N \nu_i R_{f, i}
        \end{equation}
    Where $\nu_i$ number of each species produced for each reaction.

   The second step of the computational effort simulated pyrolysis gas distribution in near the heater using OpenFOAM~\cite{Foundation2020}. The mass, momentum, species, and energy equations for the OpenFOAM calculations are shown below.
            \begin{equation}
                \pder[p]{t} + \pder [\rho u_{j}] {x_{j}} = 0
            \end{equation}

@@

            \begin{multline}
                \pder[\left(\rho h \right)]{t} + \pder[\left( \rho u_j h \right)]{x_j} + \pder[\left(  \rho k \right)]{t} + \pder[\left( \rho u_j k\right)]{x_j} = \\ -
                \pder[\left( q_i + q_{ti} \right)]{x_i} + \rho r + q_{rad} + \pder[p]{t} - \rho g_j u_j + \pder[\left( \tau_{ij} u_i \right)]{x_j}
            \end{multline}
      The computational domain used is outlined in Figure~\ref{fig:windTunnelApparatus} with a dashed rectangle. A subset of the wind tunnel test section near the heater(s) was considered for the simulation of the flow over the heater(s). For all three heater angles a constant cross section normal to the flow was used. The dimensions of the plane normal to the flow was 110\si{\milli\meter} wide and 48\si{\milli\meter} tall. The lengths of the domains varied to maintain a domain size of 5D upstream and 14D downstream of the heater. The domain lengths were 170\si{\milli\meter} for the 45\si{\degree} and parallel configurations and 120\si{\milli\meter} for the heater perpendicular to the flow. The number of cells for each domain were 420728, 424308, and 307252 for the parallel, 45\si{\degree}, and perpendicular cases. Cell sizes ranged from 0.1\si{\milli\meter} near the heater to 4\si{\milli\meter} in the bulk flow region in the center of the domain.

      The inlet boundary conditions were determined from experimental measurements where the bulk wind speed was 5.8 \si{\meter\per\second} and the inlet turbulence intensity was 0.14\%. The solid surfaces (i.e., cartridge heater, holding rods, fuel bed, and wind tunnel floor) were considered with a no-slip boundary condition and at fixed temperatures. All temperatures except the heater surfaces and pyrolyzate injection were 300\si{\kelvin}. The cartridge heater was maintained at a fixed uniform temperature corresponding to the temperature estimated to result in 50\% ignition probability from experimental tests. The inlet temperature and mass flux of the pyrolysis gases were determined from the fuel bed thermal model and Cantera calculations.  The outlet and sides of the domain used a zero gradient boundary condition. The local equivalence ratio was calculated after one second of pyrolysis release. While these times are much less than the average time to ignition, insights are still gained into the distribution of pyrolyzates with respect to the observed ignition locations for the heater orientations. For validation the separation angle of the flow was compared to a correlation from literature~\cite{Jiang2020SeparationRegime} and was found to predict the angle within 1\% of the recommended correlation. Further grid refinement did not appreciably reduce the error and resulted in a significant increase in computational time. Thus, the calculations were considered of acceptable accuracy to visualize the trends observed in experiments.

>>>>

    The temperature evolution of the fuel bed over time was used to estimate the mass of the fuel bed material undergoing pyrolysis. The calculations solved the heat diffusion equation (Equation~\ref{eqn:heatDiffusion}) to observe the spatial and temporal evolution of the fuel bed temperatures. Calculations were conducted for 10 seconds for two reasons. First, the assumptions, that are outlined in the following section, reduce the accuracy of the model due to pyrolysis of the fuel bed in the experiment changing the fuel bed properties. Second, in absence of changes in fuel beds due to pyrolysis a simulation time of ten seconds provided sufficient insight into trends observed in the experiments. 
        \begin{equation}
            \frac{\partial \left(\rho h \right)}{\partial t} = \frac{\partial}{\partial x_{j}} \left( \alpha \frac{\partial h}{\partial x_{j}} \right)
            \label{eqn:heatDiffusion}
        \end{equation}
     The assumptions for the temperature modeling of the fuel bed are as follows:
        \begin{itemize}
            \item Fuel beds were considered to be non reacting. 
            \item Thermal properties of the fuel bed were considered independent of temperature.
            \item The temperature evolution of the fuel bed is symmetric around the centerline of the heater.
            \item The heat losses to the ambient are significantly less than the heat transfer from the heater. Thus, the interface between the fuel bed and air was considered insulated.
            \item The fuel bed was modeled as a solid with the thermal and physical properties either measured or derived from measurements.
        \end{itemize}

@@

        \begin{equation}
            m \pder[\left( m Y_k \right)]{t} = \dot{m}_{k, gen} = V \dot{\omega}_k MW_k
            \label{eqn:speciesMass}
        \end{equation}
        \begin{equation}
            mc_{v} \pder[T]{t} = \dot{Q} - \sum_{k} \dot{m}_{k,gen}u_k
        \end{equation}
    Where $Y_k$, $\dot{m}_{k}$, and  $\dot{\omega}_k$ are the mass fraction, mass generation rate, and generation rate of each species $k$ in the mechanism used. $V$ is the volume of the fuel bed material in the reactor. The species generation rates $ \dot{\omega}_k$ are determined from the reactions included in the mechanism. The mechanism used for pyrolysis contains four different types of chemical reactions. The equations used to calculate the reaction rates for an elementary reaction is:
        \begin{align}
            k_f &= AT^{b}e^{-E_a/RT}\\
            R_{f} &= [A][B]k_f 
        \end{align}
    Where $R_f$ is the forward reaction rate, $k_f$ the reaction rate constant, $E_a$ the activation energy, $b$ is the temperature exponent and $R$ is the gas constant. Similarly, the reaction rates for three body reactions are calculated as:
        \begin{align}
            R_f &= [A][B][M]k_f \\
            [M] &= \sum_{k}\epsilon_k C_k
        \end{align}
    Where $\epsilon_k$ and $C_k$ are the collision efficiency and concentration of each species, respectively. Falloff reaction rates are calculated using the reduced pressure $P$ defined as:
        \begin{equation}
            P = \frac{k_0[M]}{k_\infty}
        \end{equation}
    The reaction reaction rate is then calculated as:
        \begin{equation}
            k_f (T, P) = k_{\infty} \left( \frac{P}{1+P}\right) F(T,P)
        \end{equation}
      Pressure dependent P-Log reaction rates are calculated for intermediate values using a logarithmic interpolation between two reaction rates $k_1$ and $k_2$ at pressures $P_1$ and $P_2$ as:
        \begin{equation}
            \log k_f(T,P) = \log k_1(T) + (\log k_2(T) - \log k_1(T))\frac{\log P - \log P_1}{\log P_2 - \log P_1}
        \end{equation}
  The overall generation rate of each species ($\dot{\omega}_k$) is defined as the sum of the individual reaction rates $R_f$ for all of the reactions where the species is present. Where $\nu_i$ number of each species produced for each reaction. Equation~\ref{eqn:speciesGeneration} results in the source term for Equation~\ref{eqn:speciesMass}, the solution of which determines the mass fractions of the species that are released into the fluid domain above the fuel bed.
        \begin{equation}
            \dot{\omega}_k = \sum_i^N \nu_i R_{f, i}
            \label{eqn:speciesGeneration}
        \end{equation}

   The second step of the computational effort simulated pyrolysis gas distribution in near the heater using the 3D LES solver FireFOAM implemented in OpenFOAM~\cite{Foundation2020}. The mass, momentum, species, and energy equations for the FireFOAM calculations are shown below.
            \begin{equation}
                \pder[p]{t} + \pder [\rho u_{j}] {x_{j}} = 0
            \end{equation}

@@

            \begin{multline}
                \pder[\left(\rho h \right)]{t} + \pder[\left( \rho u_j h \right)]{x_j} + \pder[\left(  \rho k \right)]{t} + \pder[\left( \rho u_j k\right)]{x_j} = \\ -
                \pder[\left( q_i + q_{ti} \right)]{x_i} + \rho r + q_{rad} + \pder[p]{t} - \rho g_j u_j + \pder[\left( \tau_{ij} u_i \right)]{x_j}
            \end{multline}
      The computational domain used is outlined in Figure~\ref{fig:windTunnelApparatus} with a dashed rectangle. A subset of the wind tunnel test section near the heater(s) was considered for the simulation of the flow over the heater(s). For all three heater angles a constant cross section normal to the flow was used. The dimensions of the plane normal to the flow was 110\si{\milli\meter} wide and 48\si{\milli\meter} high. The lengths of the domains varied to maintain a domain size of 5D upstream and 14D downstream of the heater. The domain lengths were 170\si{\milli\meter} for the 45\si{\degree} and parallel configurations and 120\si{\milli\meter} for the heater perpendicular to the flow. The number of cells for each domain were 420728, 424308, and 307252 for the parallel, 45\si{\degree}, and perpendicular cases. Cell sizes ranged from 0.1\si{\milli\meter} near the heater to 4\si{\milli\meter} in the bulk flow region in the center of the domain. For validation the separation angle of the flow was compared to a correlation from literature~\cite{Jiang2020SeparationRegime} and was found to predict the angle within 1\% of the recommended correlation. Reducing the cell size by a factor of two did not appreciably reduce the error and resulted in a significant increase in computational time. Thus, the calculations were considered of acceptable accuracy to visualize the trends observed in experiments.

      The inlet boundary conditions were determined from experimental measurements where the bulk wind speed was 5.8 \si{\meter\per\second} and the inlet turbulence intensity was 0.14\%. The solid surfaces (i.e., cartridge heater, holding rods, fuel bed, and wind tunnel floor) were considered with a no-slip boundary condition and at fixed temperatures. All temperatures except the heater surfaces and pyrolyzate injection were 300\si{\kelvin}. The cartridge heater was maintained at a fixed uniform temperature corresponding to the temperature estimated to result in 50\% ignition probability from experimental tests. The inlet temperature and mass flux of the pyrolysis gases were determined from the fuel bed thermal model and Cantera calculations.  The outlet and sides of the domain used a zero gradient boundary condition. The local equivalence ratio was calculated after one second of pyrolysis release. While one second is shorter than average time to ignition, insights are still gained into the distribution of pyrolyzates with respect to the observed ignition locations for the heater orientations.

### 2022-06-18 manuscript4.tex
Submitted version

    The thermal model of the fuel bed was conducted using OpenFOAM~\cite{Foundation2020}. The calculations solved the heat diffusion equation (Equation~\ref{eqn:heatDiffusion4} to observe the spatial and temporal evolution of the fuel bed temperatures.
        \begin{equation}
            \frac{\partial \left(\rho h \right)}{\partial t} = \frac{\partial}{\partial x_{j}} \left( \alpha \frac{\partial h}{\partial x_{j}} \right)
            \label{eqn:heatDiffusion4}
        \end{equation}

@@

        \begin{equation}
            m \pder[\left( m Y_k \right)]{t} = \dot{m}_{k, gen} = V \dot{\omega}_k MW_k
        \end{equation}
        \begin{equation}
            mc_{v} \pder[T]{t} = \dot{Q} - \sum_{k} \dot{m}_{k,gen}u_k
        \end{equation}
    Where $Y_k$, $\dot{m}_{k}$, and  $\dot{\omega}_k$ are the mass fraction, mass generation rate, and generation rate of each species $k$ in the mechanism used. $V$ is the volume of the fuel bed material in the reactor. The species generation rates $ \dot{\omega}_k$ are determined from the reactions included in the mechanism. The mechanism used for pyrolysis contains four different types of chemical reactions. The equations used to calculate the reaction rates for an elementary reaction is:
        \begin{align}
            k_f &= AT^{b}e^{-E_a/RT}\\
            R_{f} &= [A][B]k_f 
        \end{align}
    Where $R_f$ is the forward reaction rate, $k_f$ the reaction rate constant, $E_a$ the activation energy, $b$ is the temperature exponent and $R$ is the gas constant. Similarly, the reaction rates for three body reactions are calculated as:
        \begin{align}
            R_f &= [A][B][M]k_f \\
            [M] &= \sum_{k}\epsilon_k C_k
        \end{align}
    Where $\epsilon_k$ and $C_k$ are the collision efficiency and concentration of each species, respectively. Fallof reaction rates are calculated using the reduced pressure $P$ defined as:
        \begin{equation}
            P = \frac{k_0[M]}{k_\infty}
        \end{equation}
    The reaction reaction rate is then calculated as:
        \begin{equation}
            k_f (T, P) = k_{\infty} \left( \frac{P}{1+P}\right) F(T,P)
        \end{equation}
      Pressure dependent P-Log reaction rates are calculated for intermediate values using a logarithmic interpolation between two reaction rates $k_1$ and $k_2$ at pressures $P_1$ and $P_2$ as:
        \begin{equation}
            \log k_f(T,P) = \log k_1(T) + (\log k_2(T) - \log k_1(T))\frac{\log P - \log P_1}{\log P_2 - \log P_1}
        \end{equation}
    The overall generation rate of each species ($\dot{\omega}_k$) is then defined as the sum of the individual reaction rates $R_f$ for all of the reactions where the species is present. 
        \begin{equation}
            \dot{\omega}_k = \sum_i^N \nu_i R_{f, i}
        \end{equation}
    Where $\nu_i$ number of each species produced for each reaction.

@@

            \begin{multline}
                \pder[\bar{\rho}\tilde{h_s}]{t} + \pder{x_i} (\bar{\rho} \tilde{u_i} \tilde{h_s}) = \\ \bar{\dot{\omega_T}} + \frac{\bar{Dp}}{Dt} + \pder{x_i} \left( \overline{\lambda \pder[T]{x_i}} - \overline{\rho u''_i h''_s} \right) + \overline{\tau_{ij} \pder[u_i]{x_j}} - \pder{x_i} \left( \overline{\rho \sum_{k=1}^n V_{k,i} Y_k h_{s,k}} \right)
            \end{multline}
        where
            \begin{equation}
                \frac{\bar{Dp}}{Dt} = \pder[\bar{p}]{t} + \tilde{u_i} \pder[\bar{p}]{x_i}+ \overline{u''_i \pder[p]{x_i}}    
            \end{equation}
     The domain used for all calculations performed was 125\si{\milli\meter} long and 75\si{\milli\meter} high. For the cases where the heaters were spaced one diameter apart a total of 13206 cells with characteristic lengths from 0.05\si{\milli\meter} in the region surrounding the heaters to 1.5\si{\milli\meter} in the free stream above the heaters. For the cases where the heaters were spaced five diameters apart a total of 21948 cell with characteristic lengths from 0.06\si{\milli\meter} in the region surrounding the heaters to 1.6\si{\milli\meter} in the free stream above the heaters. For both cases the fine mesh spacing extended between the heaters accounting for the increased cell count for the five diameter spaced case. Further refinement of the mesh resulted in a shift in separation angle for the upstream heater of 0.2\%. Thus, the calculations were considered of acceptable accuracy to visualize the trends observed in experiments.

    The inlet boundary conditions were determined from experimental measurements where the bulk wind speeds were 5.8 \si{\meter\per\second}, 3.5 \si{\meter\per\second}, 0.5 \si{\meter\per\second} with corresponding inlet turbulence intensities of 0.14\%, 0.2\% and 1.6\% respectively. Turbulence parameters were determined from measurements taken of the experimental apparatus with a TSI IFA-300 hot wire anemometer. The k-$\epsilon$ turbulence model was used with values of 1.4$\cdot$10\textsuperscript{-4}\si{\square\meter\per\square\second} and 9.5$\cdot$10\textsuperscript{-6}\si{\square\meter\per\cubic\second} for k and $\epsilon$ respectively. Calculations were conducted for 10\si{\second} and were then averaged to observe differences in temperature and velocity characteristics between the different configurations. The solid surfaces (i.e., cartridge heater, fuel bed, and wind tunnel floor) were considered with a no-slip boundary condition at fixed temperatures. All temperatures except the heater surfaces were 300\si{\kelvin}. The inlet temperature and inlet velocity of the pyrolysis gases were determined from the fuel bed thermal model and Cantera calculations. The cartridge heater was maintained at a fixed uniform temperature corresponding to the temperature estimated to result in 50\% ignition probability from experimental tests. The outlet and tap of the domain used a zero gradient boundary condition.

>>>>

    The 2-D thermal model of the fuel bed was conducted using OpenFOAM~\cite{Foundation2020}. The calculations solved the heat diffusion equation (Equation~\ref{eqn:heatDiffusion4}) to observe the spatial and temporal evolution of the fuel bed temperatures.
        \begin{equation}
            \frac{\partial \left(\rho h \right)}{\partial t} = \frac{\partial}{\partial x_{j}} \left( \alpha \frac{\partial h}{\partial x_{j}} \right)
            \label{eqn:heatDiffusion4}
        \end{equation}

@@

        \begin{equation}
            m \pder[\left( m Y_k \right)]{t} = \dot{m}_{k, gen} = V \dot{\omega}_k MW_k
            \label{eqn:speciesMass4}
        \end{equation}
        \begin{equation}
            mc_{v} \pder[T]{t} = \dot{Q} - \sum_{k} \dot{m}_{k,gen}u_k
        \end{equation}
    Where $Y_k$, $\dot{m}_{k}$, and  $\dot{\omega}_k$ are the mass fraction, mass generation rate, and generation rate of each species $k$ in the mechanism used. $V$ is the volume of the fuel bed material in the reactor. The species generation rates $ \dot{\omega}_k$ are determined from the reactions included in the mechanism. The mechanism used for pyrolysis contains four different types of chemical reactions. The equations used to calculate the reaction rates for an elementary reaction is:
        \begin{align}
            k_f &= AT^{b}e^{-E_a/RT}\\
            R_{f} &= [A][B]k_f 
        \end{align}
    Where $R_f$ is the forward reaction rate, $k_f$ the reaction rate constant, $E_a$ the activation energy, $b$ is the temperature exponent and $R$ is the gas constant. Similarly, the reaction rates for three body reactions are calculated as:
        \begin{align}
            R_f &= [A][B][M]k_f \\
            [M] &= \sum_{k}\epsilon_k C_k
        \end{align}
    Where $\epsilon_k$ and $C_k$ are the collision efficiency and concentration of each species, respectively. Falloff reaction rates are calculated using the reduced pressure $P$ defined as:
        \begin{equation}
            P = \frac{k_0[M]}{k_\infty}
        \end{equation}
    The reaction reaction rate is then calculated as:
        \begin{equation}
            k_f (T, P) = k_{\infty} \left( \frac{P}{1+P}\right) F(T,P)
        \end{equation}
      Pressure dependent P-Log reaction rates are calculated for intermediate values using a logarithmic interpolation between two reaction rates $k_1$ and $k_2$ at pressures $P_1$ and $P_2$ as:
        \begin{equation}
            \log k_f(T,P) = \log k_1(T) + (\log k_2(T) - \log k_1(T))\frac{\log P - \log P_1}{\log P_2 - \log P_1}
        \end{equation}
  The overall generation rate of each species ($\dot{\omega}_k$) is defined as the sum of the individual reaction rates $R_f$ for all of the reactions where the species is present. Where $\nu_i$ number of each species produced for each reaction. Equation~\ref{eqn:speciesGeneration4} results in the source term for Equation~\ref{eqn:speciesMass4}, the solution of which determines the mass fractions of the species that are released into the fluid domain above the fuel bed.
        \begin{equation}
            \dot{\omega}_k = \sum_i^N \nu_i R_{f, i}
            \label{eqn:speciesGeneration4}
        \end{equation}
    Where $\nu_i$ number of each species produced for each reaction.

@@

            \begin{multline}
                \pder[\bar{\rho}\tilde{h_s}]{t} + \pder{x_i} (\bar{\rho} \tilde{u_i} \tilde{h_s}) = \\ \bar{\dot{\omega_T}} + \frac{\bar{Dp}}{Dt} + \pder{x_i} \left( \overline{\lambda \pder[T]{x_i}} - \overline{\rho u''_i h''_s} \right) + \overline{\tau_{ij} \pder[u_i]{x_j}} - \pder{x_i} \left( \overline{\rho \sum_{k=1}^n V_{k,i} Y_k h_{s,k}} \right)
            \end{multline}
        where
            \begin{equation}
                \frac{\bar{Dp}}{Dt} = \pder[\bar{p}]{t} + \tilde{u_i} \pder[\bar{p}]{x_i}+ \overline{u''_i \pder[p]{x_i}}    
            \end{equation}
     The domain used for all calculations performed was 125\si{\milli\meter} long and 75\si{\milli\meter} high. For the cases where the heaters were spaced one diameter apart a total of 13206 cells with characteristic lengths from 0.05\si{\milli\meter} in the region surrounding the heaters to 1.5\si{\milli\meter} in the free stream above the heaters. For the cases where the heaters were spaced five diameters apart a total of 21948 cell with characteristic lengths from 0.06\si{\milli\meter} in the region surrounding the heaters to 1.6\si{\milli\meter} in the free stream above the heaters. For both cases the fine mesh spacing extended between the heaters accounting for the increased cell count for the five diameter spaced case. Refinement of the mesh by a factor of three resulted in a shift in separation angle for the upstream heater of 0.2\%. Thus, the calculations were considered of acceptable accuracy to visualize the trends observed in experiments.

    The inlet boundary conditions were determined from experimental measurements where the bulk wind speeds were 5.8 \si{\meter\per\second}, 3.5 \si{\meter\per\second}, 0.5 \si{\meter\per\second} with corresponding inlet turbulence intensities of 0.14\%, 0.2\% and 1.6\% respectively. Turbulence parameters were determined from measurements taken of the experimental apparatus with a TSI IFA-300 hot wire anemometer. The k-$\epsilon$ turbulence model was used with values of 1.4$\cdot$10\textsuperscript{-4}\si{\square\meter\per\square\second} and 9.5$\cdot$10\textsuperscript{-6}\si{\square\meter\per\cubic\second} for k and $\epsilon$ respectively. Calculations were conducted for 10\si{\second} and were then averaged to observe differences in temperature and velocity characteristics between the different configurations. The solid surfaces (i.e., cartridge heater, fuel bed, and wind tunnel floor) were considered with a no-slip boundary condition at fixed temperatures. All temperatures except the heater surfaces and pyrolyzate inlets were 300\si{\kelvin}. The inlet temperature and inlet velocity of the pyrolysis gases were determined from the fuel bed thermal model and Cantera calculations. The cartridge heater was maintained at a fixed uniform temperature corresponding to the temperature estimated to result in 50\% ignition probability from experimental tests. The outlet and tap of the domain used a zero gradient boundary condition.
